Reducing iptables configuration complexity using chains

### 2014-04-20 iptables/presentation.tex
update event data
add more examples to iptables introduction

\date[Newline 0x04 29Mar2014]{Newline 0x04\\
Whitespace, Ghent\\
March 29th, 2014}

@@

      \small{-A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport http -j ACCEPT\\
      -A INPUT -j DROP}

@@

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -s 10.0.0.0/8 -j ACCEPT}

@@

@@

      \small{-A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -j DROP}

>>>>

\institute[UGent]{Ghent University, Belgium}
\date[LinuxTag 8May2014]{LinuxTag - Berlin\\
May 8th, 2014}

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport http -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      iptables -A INPUT -j DROP}

@@

      \small{iptables -A \textbf{INPUT} -m tcp -p tcp --dport ssh -j ACCEPT}

@@

      \small{iptables -A INPUT \textbf{-m tcp -p tcp --dport ssh -s 10.0.0.0/8} -j ACCEPT}

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh \textbf{-j ACCEPT}}

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      iptables -A INPUT -j DROP}
